High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition

### 2011-11-21 discussion.tex
Response to reviewer comments

Our results provide more evidence that biologically-inspired models represent a promising
and powerful direction in face recognition research. Individual models from this
class are able to achieve good performance (e.g. around 77\% for \emph{V1-like} models,
84\% for \emph{HT-L3}), and blends of these models achieve more than 88\%
correct performance, placing it amongst the best performing systems on this challenge set.

Consistent with expectations, progressively more complex, multi-layer models are
able to outperform the simpler \emph{V1-like} model. Whether this higher
performance is due to a greater ability to tolerate image variation (one of the
original purposes for the construction of the \emph{HT-L3} model
class\cite{pinto:plos09}) or some other factor remains to be seen. It should be
noted that the \emph{HT-L2} and \emph{HT-L3} models used here were substantially
simplified from those present in \cite{pinto:plos09}, in that they did not have
structured filter kernels, nor were they subjected to any unsupervised learning.
Whether adding these features back will result in higher levels of performance
is an important future research question.

>>>>

Our results provide more evidence that biologically-inspired models represent a promising
and powerful direction in face recognition research. Individual models from this
class are able to achieve good performance (e.g. around 77\% for \emph{V1-like} models,
84\% for \emph{HT-L3}), and blends of these models achieve more than 88\%
correct performance, placing it amongst the best performing systems on this challenge set.  
The model selection approach used here relies on a brute force search of a large space of candidate models, which is increasingly made feasible by the availability of recent advances in parallel computing resources, specifically graphics processing units (GPUs).  The roughly 15,000 models considered in this paper were evaluated in under one week.

Consistent with expectations, progressively more complex, multi-layer models are
able to outperform the simpler \emph{V1-like} model. Whether this higher
performance is due to a greater ability to tolerate image variation (one of the
original purposes for the construction of the \emph{HT-L3} model
class\cite{pinto:plos09}) or some other factor remains to be seen. It should be
noted that the \emph{HT-L2} and \emph{HT-L3} models used here were substantially
simplified from those present in \cite{pinto:plos09}, in that they did not have
structured filter kernels, nor were they subjected to any unsupervised learning.
Whether adding these features back will result in higher levels of performance
is an important future research question.  It should also be noted that, in terms of biological-inspiration, the model family tested here almost certainly represents just a small fraction of the complexity of the brain's visual system.  In addition, no claims are made that the three layers of the models presented here correspond in any strong way with the first three visual cortical areas.
